---
title: "11.05.2023 data cleaning (all)"
subtitle: "no subtitle"
author: "Team 3"
format: 
  html:
    self-contained: true
---

## Setup
```{r setup, include=FALSE}
library(tidyverse)
library(data.table)
library(ggplot2)
library(purrr)
library(dplyr)

library(lubridate)
```



## Reading in original data from competition org
```{r message=FALSE, warning=FALSE}
library(readr)

rawData2021 <- read_csv("data/data_2017_2021.csv")
rawData2022_2023 <- read_csv("data/data_2022_2023.csv")

```

## rawData2021: making all names bigger-case letters (for convenience down the line when we have to filter out an individual athlete)
```{r}
rawData2021$LastName <- toupper(rawData2021$LastName)
rawData2021$FirstName <- toupper(rawData2021$FirstName)

#uniqueCombinationsOfFirstAndLastNameInRawData2021 <- unique(rawData2021[, c("FirstName", "LastName")])
# uniqueCombinationsOfFirstAndLastNameInRawData2021
# was length 107
```


## rawData2021: Correcting for duplicates when they are the same athlete
```{r}
# D'AMATO, ALICE and D'AMATO, ASIA

# If the LastName is "D AMATO", change it to "D'AMATO"
rawData2021$LastName[rawData2021$LastName == "D AMATO"] <- "D'AMATO"


# JESUS SANTOS, MELANIE

# If LastName is 'JESUS SANT' or 'JESUS SANTOS' and FirstName is NA
# Make LastName as 'JESUS SANTOS' and make FirstName as 'MELANIE'
rawData2021$LastName[rawData2021$LastName == "JESUS SANT" & is.na(rawData2021$FirstName)] <- "JESUS SANTOS"
rawData2021$FirstName[rawData2021$LastName == "JESUS SANT" & is.na(rawData2021$FirstName)] <- "MELANIE"
rawData2021$FirstName[rawData2021$LastName == "JESUS SANTOS" & is.na(rawData2021$FirstName)] <- "MELANIE"

# If LastName is 'DE' and FirstName is 'JESUS'
# Make LastName as 'JESUS SANTOS' and make FirstName as 'MELANIE'
rawData2021$LastName[rawData2021$LastName == "DE" & rawData2021$FirstName == "JESUS"] <- "JESUS SANTOS"
rawData2021$FirstName[rawData2021$LastName == "DE" & rawData2021$FirstName == "JESUS"] <- "MELANIE"



# SCHAEFER BETZ, PAULINE

# If the LastName is "SCHAEFER-BETZ", change it to "SCHAEFER BETZ"
rawData2021$LastName[rawData2021$LastName == "SCHAEFER-BETZ"] <- "SCHAEFER BETZ"



#uniqueCombinationsOfFirstAndLastNameInRawData2021 <- unique(rawData2021[, c("FirstName", "LastName")])
#uniqueCombinationsOfFirstAndLastNameInRawData2021
#now is length 103



```

## rawData2021: Dates
```{r}
# function removing prefixes like SUN
removeDatePrefix <- function(date_string) {
  cleaned_string <- gsub("^[A-Z]{3} ", "", date_string)
}

rawData2021$Date <- sapply(rawData2021$Date, removeDatePrefix)



rawData2021$Date <- gsub(" JUL ", "-07-", rawData2021$Date)
rawData2021$Date <- gsub(" July ", "-07-", rawData2021$Date)
rawData2021$Date <- gsub(" Aug ", "-08-", rawData2021$Date)




# Making sure all of the Dates column is "dd-mm-yyyy"
format_dates <- function(date_str) {
  if (grepl("^\\d-\\d{2}-\\d{4}$", date_str)) {  # Check if the format is "d-mm-yyyy"
    parts <- unlist(strsplit(date_str, "-"))
    return(paste0(sprintf("%02d", as.numeric(parts[1])),
                  "-",
                  sprintf("%02d", as.numeric(parts[2])),
                  "-",
                  parts[3]))
  } else {
    return(date_str)
  }
}

rawData2021$Date <- sapply(rawData2021$Date, format_dates)


#class(rawData2021$Date)
```



## rawData2021: Penalty
```{r}
# Change any NA's in the Penalty column to zero
rawData2021$Penalty[is.na(rawData2021$Penalty)] <- 0
```





## rawData2021: NA's
```{r}
NAsInrawData2021 <- rawData2021 %>%
  filter(is.na(Rank) | is.na(D_Score) | is.na(E_Score))

# To view the filtered dataframe
print(NAsInrawData2021)
```
NOTE: now, the NA's in rawData2021 just mean no attempt
NOTE: there are two rows that say Apparatus is UE, which is not an event for women... it should be UB...?


## rawData2021 cleaning done -> NOW CALLED data2021Female
```{r}
data2021Female <- rawData2021
```













## rawData2022_2023: making all names bigger-case letters (for convenience down the line when we have to filter out an individual athlete)
```{r}
rawData2022_2023$LastName <- toupper(rawData2022_2023$LastName)
rawData2022_2023$FirstName <- toupper(rawData2022_2023$FirstName)

#uniqueCombinationsOfFirstAndLastNameInRawData2022_2023 <- unique(rawData2022_2023[, c("FirstName", "LastName")])
# uniqueCombinationsOfFirstAndLastNameInRawData2022_2023
# was length 1824
```

## rawData2022_2023: Correcting for duplicates when they are the same athlete (did until last name G!)
```{r}
# AAS, FREDRIK BJORNEVIK

# If the FirstName is "FREDRIK BJORNEVIK", change it to "FREDRIK"
rawData2022_2023$FirstName[rawData2022_2023$FirstName == "FREDRIK BJORNEVIK"] <- "FREDRIK"


# Athlete ABIYURAFI (Last Name) just does not have a first name in any competition, so change his first name to simply ""
rawData2022_2023$FirstName[rawData2022_2023$LastName == "ABIYURAFI" & is.na(rawData2022_2023$FirstName)] <- ""



# MISELLA ANTILA
rawData2022_2023$FirstName[rawData2022_2023$FirstName == "MISELLA ALLI HELENA" & rawData2022_2023$LastName == "ANTILA"] <- "MISELLA"


# ANTON YEFFERSON
rawData2022_2023$FirstName[rawData2022_2023$LastName == "ANTON YEGUEZ" & rawData2022_2023$FirstName == "YEFFERSON GREGORIO"] <- "YEFFERSON"
rawData2022_2023$LastName[rawData2022_2023$LastName == "ANTON YEGUEZ" & rawData2022_2023$FirstName == "YEFFERSON GREGORIO"] <- "ANTON"
rawData2022_2023$LastName[rawData2022_2023$LastName == "ANTON YEGUEZ" & rawData2022_2023$FirstName == "YEFFERSON"] <- "ANTON"


# MIGUEL AQUINO III
rawData2022_2023$FirstName[rawData2022_2023$FirstName == "MIGUEL ANGEL" & rawData2022_2023$LastName == "AQUINO III"] <- "MIGUEL"

# SYDNEY TATIANA BARROS FROM PUR IS DIFFERENT FROM SYDNEY TATIANA FROM USA
rawData2022_2023$FirstName[rawData2022_2023$FirstName == "SYDNEY" & 
                           rawData2022_2023$LastName == "BARROS" & 
                           rawData2022_2023$Country == "PUR"] <- "SYDNEY TATIANA"




# CAMERON-LIE BERNARD
rawData2022_2023$FirstName[rawData2022_2023$FirstName == "CAMERON LIE" & rawData2022_2023$LastName == "BERNARD"] <- "CAMERON-LIE"



# JUANCHO BESANA
rawData2022_2023$FirstName[rawData2022_2023$FirstName == "JUANCHO MIGUEL" & rawData2022_2023$LastName == "BESANA"] <- "JUANCHO"


# VICTOR BETANCOURT
rawData2022_2023$FirstName[rawData2022_2023$FirstName == "VICTOR MANUEL" & rawData2022_2023$LastName == "BETANCOURT QUINTANA"] <- "VICTOR"
rawData2022_2023$LastName[rawData2022_2023$FirstName == "VICTOR MANUEL" & rawData2022_2023$LastName == "BETANCOURT QUINTANA"] <- "BETANCOURT"
rawData2022_2023$LastName[rawData2022_2023$FirstName == "VICTOR" & rawData2022_2023$LastName == "BETANCOURT QUINTANA"] <- "BETANCOURT"



# KRISTOPHER BOHORQUEZ
rawData2022_2023$FirstName[rawData2022_2023$FirstName == "KRISTOPHER STEVEN" & rawData2022_2023$LastName == "BOHORQUEZ CANTOR"] <- "KRISTOPHER"
rawData2022_2023$LastName[rawData2022_2023$FirstName == "KRISTOPHER STEVEN" & rawData2022_2023$LastName == "BOHORQUEZ CANTOR"] <- "BOHORQUEZ"
rawData2022_2023$LastName[rawData2022_2023$FirstName == "KRISTOPHER" & rawData2022_2023$LastName == "BOHORQUEZ CANTOR"] <- "BOHORQUEZ"


# VALENTINA BROSTELLA
rawData2022_2023$LastName[rawData2022_2023$FirstName == "VALENTINA" & rawData2022_2023$LastName == "BROSTELLA ARIAS"] <- "BROSTELLA"


# non-alphabetic
rawData2022_2023$LastName[rawData2022_2023$LastName == "BÖCZÖGÖ"] <- "BOCZOGO"


# JOSSIMAR ORLANDO   CALVO MORENO
rawData2022_2023$LastName[is.na(rawData2022_2023$FirstName) & rawData2022_2023$LastName == "CALVO MORENO JO"] <- "CALVO MORENO"


rawData2022_2023$FirstName[rawData2022_2023$FirstName == "SABRINA ALESSANDRA" & 
                           rawData2022_2023$LastName == "CARDERO"] <- "SABRINA"


rawData2022_2023$LastName[rawData2022_2023$FirstName == "JAN" & 
                          rawData2022_2023$LastName == "CARRERES MACIA"] <- "CARRERES"

rawData2022_2023$FirstName[rawData2022_2023$FirstName == "JOSEPH" & 
                           rawData2022_2023$LastName == "CEMLYN JONES"] <- "JOE"

rawData2022_2023$FirstName[rawData2022_2023$FirstName == "CARMINA ISABELLA" & 
                           rawData2022_2023$LastName == "CHAVEZ MARTINEZ"] <- "CARMINA"

rawData2022_2023$LastName[rawData2022_2023$FirstName == "CARMINA" & 
                          rawData2022_2023$LastName == "CHAVEZ MARTINEZ"] <- "CHAVEZ"


rawData2022_2023$FirstName[rawData2022_2023$FirstName == "ZACHARY NATHANIEL" & 
                           rawData2022_2023$LastName == "CLAY"] <- "ZACHARY"




rawData2022_2023$FirstName[rawData2022_2023$FirstName == "WILFRY MANUEL" & 
                           rawData2022_2023$LastName == "CONTRERAS"] <- "WILFRY"




rawData2022_2023 <- rawData2022_2023 %>%
  mutate(
    FirstName = ifelse(FirstName == 'JHOSSUA ARIEL' & LastName == 'CORRALES CASTRO', 'JHOSSUA', FirstName),
    LastName = ifelse(FirstName == 'JHOSSUA ARIEL' & LastName == 'CORRALES CASTRO', 'CORRALES', LastName)
  )


rawData2022_2023$FirstName[rawData2022_2023$FirstName == "MATTHEW" & 
                           rawData2022_2023$LastName == "CORMIER"] <- "MATT"



rawData2022_2023$LastName[rawData2022_2023$FirstName == "ALEJANDRO" & 
                          rawData2022_2023$LastName == "DE LA CRUZ GATO"] <- "DE LA CRUZ"



rawData2022_2023$FirstName[rawData2022_2023$FirstName == "FABIÁN"] <- "FABIAN"
rawData2022_2023$LastName[rawData2022_2023$FirstName == "FABIAN" & 
                          rawData2022_2023$LastName == "DE LUNA HERNÁNDEZ"] <- "DE LUNA"



rawData2022_2023$FirstName[rawData2022_2023$FirstName == "NATALIA GABRIELA" & 
                           rawData2022_2023$LastName == "DELGADO LOPEZ"] <- "NATALIA"
rawData2022_2023$LastName[rawData2022_2023$FirstName == "NATALIA" & 
                           rawData2022_2023$LastName == "DELGADO LOPEZ"] <- "DELGADO"


rawData2022_2023$FirstName[rawData2022_2023$FirstName == "STELLA LOREN" & 
                           rawData2022_2023$LastName == "DIAZ"] <- "STELLA"


rawData2022_2023$LastName[rawData2022_2023$FirstName == "KARELYS" & 
                          rawData2022_2023$LastName == "DIAZ DAVILA"] <- "DIAZ"



rawData2022_2023$FirstName[rawData2022_2023$FirstName == "JACOB GUEST" & 
                           rawData2022_2023$LastName == "DWARDS"] <- "JACOB"



rawData2022_2023$FirstName[is.na(rawData2022_2023$FirstName) & 
                           rawData2022_2023$LastName == "ELPITIYA BADALG D"] <- "MILKA GEHANI"
rawData2022_2023$LastName[rawData2022_2023$FirstName == "MILKA GEHANI" & 
                          rawData2022_2023$LastName == "ELPITIYA BADALGE DONA"] <- "ELPITIYA BADALGE D"



rawData2022_2023$FirstName[rawData2022_2023$FirstName == "NATALIA ISABEL" & 
                           rawData2022_2023$LastName == "ESCALERA"] <- "NATALIA"


rawData2022_2023$LastName[rawData2022_2023$FirstName == "JOSE CARLOS" & 
                          rawData2022_2023$LastName == "ESCANDÓN MARÍN"] <- "ESCANDON MARIN"
rawData2022_2023$LastName[rawData2022_2023$FirstName == "JOSE" & 
                          rawData2022_2023$LastName == "ESCANDON"] <- "ESCANDON MARIN"
rawData2022_2023$FirstName[rawData2022_2023$FirstName == "JOSE" & 
                          rawData2022_2023$LastName == "ESCANDON"] <- "JOSE CARLOS"


rawData2022_2023$LastName[rawData2022_2023$FirstName == "GINNA" & 
                          rawData2022_2023$LastName == "ESCOBAR BETANCUR"] <- "ESCOBAR"


rawData2022_2023$LastName[rawData2022_2023$FirstName == "KEVIN" & 
                          rawData2022_2023$LastName == "ESPINOSA CASTILLO"] <- "ESPINOSA"


rawData2022_2023$FirstName[rawData2022_2023$FirstName == "SEBASTIAN NORBERT" & 
                           rawData2022_2023$LastName == "GAWRONSKI"] <- "SEBASTIAN"

rawData2022_2023$FirstName[rawData2022_2023$FirstName == "EDWARD ANDRE" & 
                           rawData2022_2023$LastName == "GONZALES RIVAS"] <- "EDWARD"

rawData2022_2023$LastName[rawData2022_2023$FirstName == "EDWARD" & 
                           rawData2022_2023$LastName == "GONZALES"] <- "EDWARD"

rawData2022_2023$FirstName[rawData2022_2023$FirstName == "ALEXA GABRIELA" & 
                           rawData2022_2023$LastName == "GRANDE FRANCO"] <- "ALEXA"

rawData2022_2023$LastName[rawData2022_2023$FirstName == "ALEXA" & 
                           rawData2022_2023$LastName == "GRANDE FRANCO"] <- "GRANDE"

rawData2022_2023$LastName[rawData2022_2023$FirstName == "JERMAIN" & 
                           rawData2022_2023$LastName == "GRÜNBERG"] <- "GRUENBERG"

rawData2022_2023$FirstName[rawData2022_2023$FirstName == "HILDUR MAJA" & 
                           rawData2022_2023$LastName == "GUDMUNDSDOTTIR"] <- "HILDUR"

rawData2022_2023$LastName[rawData2022_2023$FirstName == "YURI" & 
                           rawData2022_2023$LastName == "GUIMARÃES"] <- "GUIMARAES"


rawData2022_2023$FirstName[rawData2022_2023$FirstName == "NELSON ALBERTO" & 
                           rawData2022_2023$LastName == "GUILBE MORALES"] <- "NELSON"

rawData2022_2023$LastName[rawData2022_2023$FirstName == "NELSON" & 
                           rawData2022_2023$LastName == "GUILBE MORALES"] <- "GUILBE"



## functions after Emily decided she had enough

rawData2022_2023 <- rawData2022_2023 %>% 
  mutate(FirstName = word(FirstName, 1)) %>% 
  mutate(LastName = word(LastName, 1))

replace_letters <- function(name) {
  name <- gsub("Ö", "OE", name)
  name <- gsub("Ü", "U", name)
  name <- gsub("Ø", "O", name)
  name <- sub("-.*", "", name)
  name <- gsub("Ä", "AE", name)
}

rawData2022_2023$FirstName <- lapply(rawData2022_2023$FirstName, replace_letters)

rawData2022_2023$LastName <- lapply(rawData2022_2023$LastName, replace_letters)

standardize <- function(name) {
  name <- iconv(name, "UTF-8", "ASCII//TRANSLIT")
}

rawData2022_2023$FirstName <- lapply(rawData2022_2023$FirstName, standardize)

rawData2022_2023$LastName <- lapply(rawData2022_2023$LastName, standardize)


## restart of emily's mutations

rawData2022_2023$FirstName[rawData2022_2023$FirstName == "RAKAH" & 
                           rawData2022_2023$LastName == "HARITHI"] <- "RAKAN"


rawData2022_2023$LastName[rawData2022_2023$FirstName == "VINCENZ" & 
                           rawData2022_2023$LastName == "HOCK"] <- "HOECK"

rawData2022_2023$FirstName[rawData2022_2023$FirstName == "MOHAMAD" & 
                           rawData2022_2023$LastName == "KHALIL"] <- "MOHAMED"

rawData2022_2023$LastName[rawData2022_2023$FirstName == "SEVERIN" & 
                           rawData2022_2023$LastName == "KRANZLMULLER"] <- "KRANZLMUELLER"
                           
rawData2022_2023$FirstName[rawData2022_2023$FirstName == "MANUEL" & 
                           rawData2022_2023$LastName == "MARTINEZ"] <- "JOSE"

rawData2022_2023$FirstName[rawData2022_2023$FirstName == "FELIPE" & 
                           rawData2022_2023$LastName == "MARTINEZ"] <- "ANDRES"

rawData2022_2023$LastName[rawData2022_2023$FirstName == "CLAY" & 
                           rawData2022_2023$LastName == "MASON"] <- "MASONSTEPHENS"

rawData2022_2023$LastName[rawData2022_2023$FirstName == "MC" & 
                           rawData2022_2023$LastName == "ATEER"] <- "MCATEER"

rawData2022_2023$FirstName[rawData2022_2023$FirstName == "MC" & 
                           rawData2022_2023$LastName == "MCATEER"] <- "EWAN"

rawData2022_2023$LastName[rawData2022_2023$FirstName == "EWAN" & 
                           rawData2022_2023$LastName == "MC"] <- "MCATEER"


rawData2022_2023$LastName[rawData2022_2023$FirstName == "MC" & 
                           rawData2022_2023$LastName == "CLENAGHAN"] <- "MCCLENAGHAN"

rawData2022_2023$FirstName[rawData2022_2023$FirstName == "MC" & 
                           rawData2022_2023$LastName == "MCCLENAGHAN"] <- "RHYS"

rawData2022_2023$LastName[rawData2022_2023$FirstName == "RUBY" & 
                           rawData2022_2023$LastName == "EVAN"] <- "EVANS"

rawData2022_2023$LastName[rawData2022_2023$FirstName == "WONG" & 
                           rawData2022_2023$LastName == "VANESSA"] <- "WONG"

rawData2022_2023$FirstName[rawData2022_2023$FirstName == "WONG" & 
                           rawData2022_2023$LastName == "WONG"] <- "VANESSA"


rawData2022_2023$LastName[rawData2022_2023$FirstName == "LIU" & 
                           rawData2022_2023$LastName == "MAI"] <- "LIU"

rawData2022_2023$FirstName[rawData2022_2023$FirstName == "LIU" & 
                           rawData2022_2023$LastName == "LIU"] <- "MAI"

rawData2022_2023$LastName[rawData2022_2023$FirstName == "CHRISTINA" & 
                           rawData2022_2023$LastName == "KIOSO"] <- "VASILOPOULOU"

rawData2022_2023$LastName[rawData2022_2023$FirstName == "KORKEM" & 
                           rawData2022_2023$LastName == "YEROBSSYNKYZY"] <- "YERBOSSYNKYZY"

rawData2022_2023$LastName[rawData2022_2023$FirstName == "LARASATI" & 
                           rawData2022_2023$LastName == "REGGANIS"] <- "RENGGANIS"


uniqueCombinationsOfFirstAndLastNameInRawData2022_2023 <- unique(rawData2022_2023[, c("FirstName", "LastName")])


```

##CLEANING COUNTRIES

```{r}
rawData2022_2023 <- rawData2022_2023 %>% 
  mutate(
    Country = case_when(Country == "SCO" ~ "GBR",
                        Country == "ENG" ~ "GBR",
                        Country == "WAL" ~ "GBR",
                        Country == "SIN" ~ "SIG",
                        Country == "GE1" ~ "GER",
                        Country == "GE2" ~ "GER",
                        Country == "NIR" ~ "GBR",
                        Country == "IOM" ~ "GBR", 
                        Country == "PUR" ~ "USA",
                        TRUE ~ Country)
  )

rawData2022_2023 <- rawData2022_2023 %>% 
  mutate(
    Country = ifelse(FirstName == "TEJA" & LastName == "BELAK", "SLO", Country),
    Country = ifelse(FirstName == "NAVEEN" & LastName == "DARIES", "RSA", Country),
    Country = ifelse(FirstName == "MADELEINE" & LastName == "MARSHALL", "NZL", Country)
  )

```


```{r}

```

