---
title: "Elyse EDA Updated"
author: "Elyse McFalls"
date: "2023-11-09"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
```

```{r}
library(tidyverse)
```


Notes:
1. Do we want to consider different scenarios (i.e., the best US team when all of our players perform at their worst and everyone else performs at their best)
  - the graphs show different medal placements based on each person's average, best, and worst scores

## Loading Data

```{r}
women <- read.csv('cleaned data/restricted_women_2023.csv')
men <- read.csv('cleaned data/restricted_men_2023.csv')
all <- read.csv('cleaned data/full_data_2023.csv')
```

## Trying Weights
Exponential rate of decay

[Article](https://jackbakerds.com/posts/upweight-recent-observations-regression-classification/)
[Paper on Weighting for Pathogen Data](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7774545/)

$$w_{ij} = \alpha^{T_i-t_{ij}} \text{, where } T_i \text{ is the most recent time (in days) for athlete i and } t_{ij} \text{ is the jth recorded time (in days) for the ith athlete}$$

```{r}
women <- women %>%
  group_by(FullName) %>%
  mutate(last_comp = max(Date)) %>%
  ungroup() %>%
  mutate(time_diff = as.numeric(difftime(last_comp, Date, units = "days")), 
         weight_95 = 0.95**time_diff, weight_90 = 0.90**time_diff) 

head(women)  
```


## Women's Data

### Vault

```{r}
women_vt <- women%>%
  filter(stringr::str_like(Apparatus,'VT%') & Rank <= 5)

women_vt_all <- all%>%
  filter(Gender == 'w' & stringr::str_like(Apparatus,'VT%'))
```

#### Number of Gymnasts by Rank (VT)
```{r}
rank_curve_vt <- function(r){
  women_vt_all %>%
    filter(Rank <= r & Country == 'USA') %>%
    distinct(FullName) %>%
    summarise(n = n()) %>%
    pull()
}
```

```{r}
ranks = seq(10, 1, -1)
athletes_vt = c()

for (rank in ranks){
  count = rank_curve_vt(rank)
  athletes_vt = c(athletes_vt, count)
}
```

```{r}
plot(x = ranks, y = athletes_vt, type = 'b', xlim = rev(range(ranks)), main = "Number of USA Athletes Who've Placed \n at each Rank or Higher for Vault (2022-2023)", ylab = "Number of Athletes")
abline(v = 3, col = "red")
abline(v = 5, col = "blue")
text(x=6, y=5, 'Simulation \n cutoff', col = 'blue')
text(x=3.75, y=5, 'Medal \n cutoff', col = 'red')
```



#### Distributions for top 5 Gymnasts

```{r}
women_vt %>%
  filter(Country == 'USA') %>%
  ggplot(aes(x = Score)) +
  geom_histogram() +
  geom_density(aes(weight = weight_95), color = "red") +
  facet_wrap(~FullName)
```


#### Best Gymnasts per Country

```{r}
# best average scores
women_vt_summary <- women_vt %>%
  group_by(FullName, Country) %>%
  summarise(avg_score = mean(Score), min_score = min(Score), max_score = max(Score)) 

head(women_vt_summary)
```

```{r fig.width=20, fig.height=10}
# top 3 avg score
women_vt_summary %>%
  group_by(Country) %>%
  arrange(desc(avg_score)) %>%
  slice(1:3) %>%
  ungroup() %>%
  arrange(desc(avg_score)) %>%
  mutate(top5 = ifelse(row_number() <= 5, row_number(), NA), top5 = as.factor(top5)) %>%
  ggplot(aes(y= reorder(FullName, avg_score), x = avg_score, fill = top5)) +
  geom_col(stat = "identity") +
  labs(title = "Top 3 Female Athletes per Country by Average Valut Score (2022-2023)") +
  facet_wrap(~factor(Country, unique(Country)), ncol = 3, scales = "free_y") 

```

```{r fig.width=20, fig.height=10}
# top 3 avg score
women_vt_summary %>%
  group_by(Country) %>%
  arrange(desc(max_score)) %>%
  slice(1:3) %>%
  ungroup() %>%
  arrange(desc(max_score)) %>%
  mutate(top5 = ifelse(row_number() <= 5, row_number(), NA), top5 = as.factor(top5)) %>%
  ggplot(aes(y= reorder(FullName, max_score), x = max_score, fill = top5)) +
  geom_col(stat = "identity") +
  labs(title = "Top 3 Female Athletes per Country by Best Valut Score (2022-2023)") +
  facet_wrap(~factor(Country, unique(Country)), ncol = 3, scales = "free_y") 
```


```{r fig.width=20, fig.height=10}
# top 3 avg score
women_vt_summary %>%
  group_by(Country) %>%
  arrange(desc(min_score)) %>%
  slice(1:3) %>%
  ungroup() %>%
  arrange(desc(min_score)) %>%
  mutate(top5 = ifelse(row_number() <= 5, row_number(), NA), top5 = as.factor(top5)) %>%
  ggplot(aes(y= reorder(FullName, min_score), x = min_score, fill = top5)) +
  geom_col(stat = "identity") +
  labs(title = "Top 3 Female Athletes per Country by Worst Valut Score (2022-2023)") +
  facet_wrap(~factor(Country, unique(Country)), ncol = 3, scales = "free_y") 
```





### Balance Beam

```{r}
women_bb <- women%>%
  filter(stringr::str_like(Apparatus,'BB%'))

women_bb_all <- all%>%
  filter(Gender == 'w' & stringr::str_like(Apparatus,'BB%'))
```

*Number of Gymnasts by Rank (BB)*
```{r}
rank_curve_bb <- function(r){
  women_bb_all %>%
    filter(Rank <= r & Country == 'USA') %>%
    distinct(FullName) %>%
    summarise(n = n()) %>%
    pull()
}
```

```{r}
ranks = seq(10, 1, -1)
athletes_bb = c()

for (rank in ranks){
  count = rank_curve_bb(rank)
  athletes_bb = c(athletes_bb, count)
}
```

```{r}
plot(x = ranks, y = athletes_bb, type = 'b', xlim = rev(range(ranks)), main = "Number of USA Athletes Who've Placed \n at each Rank or Higher for Balance Beam (2022-2023)", ylab = "Number of Athletes")
abline(v = 3, col = "red")
abline(v = 5, col = "blue")
text(x=6, y=10, 'Simulation \n cutoff', col = 'blue')
text(x=3.75, y=10, 'Medal \n cutoff', col = 'red')
```


*Best Gymnasts per Country*

```{r}
# best average scores
women_bb_summary <- women_bb %>%
  group_by(FullName, Country) %>%
  summarise(avg_score = mean(Score), min_score = min(Score), max_score = max(Score)) 

head(women_bb_summary)
```

```{r fig.width=20, fig.height=10}
# top 3 avg score
women_bb_summary %>%
  group_by(Country) %>%
  arrange(desc(avg_score)) %>%
  slice(1:3) %>%
  ungroup() %>%
  arrange(desc(avg_score)) %>%
  mutate(top5 = ifelse(row_number() <= 5, row_number(), NA), top5 = as.factor(top5)) %>%
  ggplot(aes(y= reorder(FullName, avg_score), x = avg_score, fill = top5)) +
  geom_col(stat = "identity") +
  labs(title = "Top 3 Female Athletes per Country by Average Balance Beam Score (2022-2023)") +
  facet_wrap(~factor(Country, unique(Country)), ncol = 3, scales = "free_y") 

```

```{r fig.width=20, fig.height=10}
# top 3 avg score
women_bb_summary %>%
  group_by(Country) %>%
  arrange(desc(max_score)) %>%
  slice(1:3) %>%
  ungroup() %>%
  arrange(desc(max_score)) %>%
  mutate(top5 = ifelse(row_number() <= 5, row_number(), NA), top5 = as.factor(top5)) %>%
  ggplot(aes(y= reorder(FullName, max_score), x = max_score, fill = top5)) +
  geom_col(stat = "identity") +
  labs(title = "Top 3 Female Athletes per Country by Best Balance Beam Score (2022-2023)") +
  facet_wrap(~factor(Country, unique(Country)), ncol = 3, scales = "free_y") 
```


```{r fig.width=20, fig.height=10}
# top 3 avg score
women_bb_summary %>%
  group_by(Country) %>%
  arrange(desc(min_score)) %>%
  slice(1:3) %>%
  ungroup() %>%
  arrange(desc(min_score)) %>%
  mutate(top5 = ifelse(row_number() <= 5, row_number(), NA), top5 = as.factor(top5)) %>%
  ggplot(aes(y= reorder(FullName, min_score), x = min_score, fill = top5)) +
  geom_col(stat = "identity") +
  labs(title = "Top 3 Female Athletes per Country by Worst Balance Beam Score (2022-2023)") +
  facet_wrap(~factor(Country, unique(Country)), ncol = 3, scales = "free_y") 
```


### Floor Exercises 

```{r}
women_fx <- women%>%
  filter(stringr::str_like(Apparatus,'FX%'))
women_fx_all <- all%>%
  filter(Gender == 'w' & stringr::str_like(Apparatus,'FX%'))
```

*Number of Gymnasts by Rank (FX)*
```{r}
rank_curve_fx <- function(r){
  women_fx_all %>%
    filter(Rank <= r & Country == 'USA') %>%
    distinct(FullName) %>%
    summarise(n = n()) %>%
    pull()
}
```

```{r}
ranks = seq(10, 1, -1)
athletes_fx = c()

for (rank in ranks){
  count = rank_curve_fx(rank)
  athletes_fx = c(athletes_fx, count)
}
```

```{r}
plot(x = ranks, y = athletes_fx, type = 'b', xlim = rev(range(ranks)), main = "Number of USA Athletes Who've Placed \n at each Rank or Higher for Floor (2022-2023)", ylab = "Number of Athletes")
abline(v = 3, col = "red")
abline(v = 5, col = "blue")
text(x=6, y=10, 'Simulation \n cutoff', col = 'blue')
text(x=3.75, y=10, 'Medal \n cutoff', col = 'red')
```

*Best Gymnasts per Country*

```{r}
# best average scores
women_fx_summary <- women_fx %>%
  group_by(FullName, Country) %>%
  summarise(avg_score = mean(Score), min_score = min(Score), max_score = max(Score)) 

head(women_fx_summary)
```

```{r fig.width=20, fig.height=10}
# top 3 avg score
women_fx_summary %>%
  group_by(Country) %>%
  arrange(desc(avg_score)) %>%
  slice(1:3) %>%
  ungroup() %>%
  arrange(desc(avg_score)) %>%
  mutate(top5 = ifelse(row_number() <= 5, row_number(), NA), top5 = as.factor(top5)) %>%
  ggplot(aes(y= reorder(FullName, avg_score), x = avg_score, fill = top5)) +
  geom_col(stat = "identity") +
  labs(title = "Top 3 Female Athletes per Country by Average Floor Score (2022-2023)") +
  facet_wrap(~factor(Country, unique(Country)), ncol = 3, scales = "free_y") 

```

```{r fig.width=20, fig.height=10}
# top 3 max score
women_fx_summary %>%
  group_by(Country) %>%
  arrange(desc(max_score)) %>%
  slice(1:3) %>%
  ungroup() %>%
  arrange(desc(max_score)) %>%
  mutate(top5 = ifelse(row_number() <= 5, row_number(), NA), top5 = as.factor(top5)) %>%
  ggplot(aes(y= reorder(FullName, max_score), x = max_score, fill = top5)) +
  geom_col(stat = "identity") +
  labs(title = "Top 3 Female Athletes per Country by Best Floor Score (2022-2023)") +
  facet_wrap(~factor(Country, unique(Country)), ncol = 3, scales = "free_y") 
```


```{r fig.width=20, fig.height=10}
# top 3 min score
women_fx_summary %>%
  group_by(Country) %>%
  arrange(desc(min_score)) %>%
  slice(1:3) %>%
  ungroup() %>%
  arrange(desc(min_score)) %>%
  mutate(top5 = ifelse(row_number() <= 5, row_number(), NA), top5 = as.factor(top5)) %>%
  ggplot(aes(y= reorder(FullName, min_score), x = min_score, fill = top5)) +
  geom_col(stat = "identity") +
  labs(title = "Top 3 Female Athletes per Country by Worst Balance Beam Score (2022-2023)") +
  facet_wrap(~factor(Country, unique(Country)), ncol = 3, scales = "free_y") 
```



### Uneven Bars

```{r}
women_ub <- women%>%
  filter(stringr::str_like(Apparatus,'UB%'))
women_ub_all <- all%>%
  filter(Gender == 'w' & stringr::str_like(Apparatus,'UB%'))
```

*Number of Gymnasts by Rank (FX)*
```{r}
rank_curve_ub <- function(r){
  women_ub_all %>%
    filter(Rank <= r & Country == 'USA') %>%
    distinct(FullName) %>%
    summarise(n = n()) %>%
    pull()
}
```

```{r}
ranks = seq(10, 1, -1)
athletes_ub = c()

for (rank in ranks){
  count = rank_curve_ub(rank)
  athletes_ub = c(athletes_ub, count)
}
```

```{r}
plot(x = ranks, y = athletes_ub, type = 'b', xlim = rev(range(ranks)), main = "Number of USA Athletes Who've Placed \n at each Rank or Higher for Uneven Bars (2022-2023)", ylab = "Number of Athletes")
abline(v = 3, col = "red")
abline(v = 5, col = "blue")
text(x=6, y=10, 'Simulation \n cutoff', col = 'blue')
text(x=3.75, y=10, 'Medal \n cutoff', col = 'red')
```

*Best Gymnasts per Country*

```{r}
# best average scores
women_ub_summary <- women_ub %>%
  group_by(FullName, Country) %>%
  summarise(avg_score = mean(Score), min_score = min(Score), max_score = max(Score)) 

head(women_ub_summary)
```

```{r fig.width=20, fig.height=10}
# top 3 avg score
women_ub_summary %>%
  group_by(Country) %>%
  arrange(desc(avg_score)) %>%
  slice(1:3) %>%
  ungroup() %>%
  arrange(desc(avg_score)) %>%
  mutate(top5 = ifelse(row_number() <= 5, row_number(), NA), top5 = as.factor(top5)) %>%
  ggplot(aes(y= reorder(FullName, avg_score), x = avg_score, fill = top5)) +
  geom_col(stat = "identity") +
  labs(title = "Top 3 Female Athletes per Country by Average Uneven Bars Score (2022-2023)") +
  facet_wrap(~factor(Country, unique(Country)), ncol = 3, scales = "free_y") 

```

```{r fig.width=20, fig.height=10}
# top 3 max score
women_ub_summary %>%
  group_by(Country) %>%
  arrange(desc(max_score)) %>%
  slice(1:3) %>%
  ungroup() %>%
  arrange(desc(max_score)) %>%
  mutate(top5 = ifelse(row_number() <= 5, row_number(), NA), top5 = as.factor(top5)) %>%
  ggplot(aes(y= reorder(FullName, max_score), x = max_score, fill = top5)) +
  geom_col(stat = "identity") +
  labs(title = "Top 3 Female Athletes per Country by Best Uneven Bars Score (2022-2023)") +
  facet_wrap(~factor(Country, unique(Country)), ncol = 3, scales = "free_y") 
```


```{r fig.width=20, fig.height=10}
# top 3 min score
women_ub_summary %>%
  group_by(Country) %>%
  arrange(desc(min_score)) %>%
  slice(1:3) %>%
  ungroup() %>%
  arrange(desc(min_score)) %>%
  mutate(top5 = ifelse(row_number() <= 5, row_number(), NA), top5 = as.factor(top5)) %>%
  ggplot(aes(y= reorder(FullName, min_score), x = min_score, fill = top5)) +
  geom_col(stat = "identity") +
  labs(title = "Top 3 Female Athletes per Country by Worst Uneven Bars Score (2022-2023)") +
  facet_wrap(~factor(Country, unique(Country)), ncol = 3, scales = "free_y") 
```












