---
title: "Elyse EDA"
author: "Elyse McFalls and Holly Cui"
date: "2023-11-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

```{r}
library(ggh4x)
```

## Questions/Comments
1. How can we tell what apparatus each all-around score relates to?
2. How will we create a model to predict the past competitions? The data we have from the newest set only contains 2022-2023 data and the older dataset only has data from the 2021 Olympics for women (only 4 have played/placed in top 5 in 2022/2023)
  a. Will need to get data for the current athletes 
3. Looks like we're dealing with sparse functional data 
4. Could predict a player's potential by comparing them to another player (i.e., we would find historically successful Olympic teams and see which current USA players are more similar to them) [link](https://onlinelibrary.wiley.com/doi/full/10.1002/sam.11436)
4. Instead of testing our model on these players, we should test it on other players that we can get a lot of data on (this paper tests their NBA points model by using players that retired  [link](https://docplayer.net/39444957-Forecasting-nba-player-performance-using-a-weibull-gamma-statistical-timing-model-abstract.html)) 
  a. paper also mentioned a Weibull-Gamma model to take into account time and used the covariate of if the player was having and off year or not (off being that they were injured)
5. Could use sparse functional data algorithms (i.e., ROPES and PACE)
  a. may be better since 1) gymnasts' careers aren't that long and 2) the point system changes every olympic season (or could add a covariate due to what cycle it is?)
  b. requires using the data from every observation to make the functions for player which may pull their predictions towards the mean -> the paper overcame this by finding players similar to the player of interest and use that data for predictions, "method of analogues." Found related players using ADA

### Assumptions
1. An athlete won't change their difficulty score since their last competition 
2. An athlete won't get tired (so they can partake in any competition they are eligible for)
3. An athlete who hasn't made the top 5 in any prior competition will not place in the olympics 
  a. use looser criteria for other countries because they may not rank high, but they will represent their country

```{r}
rawData2022_2023 %>%
  
```

```{r}
# data from Emily
df23 <- rawData2022_2023 %>%
  mutate(Date = sapply(strsplit(as.character(Date), "-"), tail, 1),
         Date = trimws(Date),                 # Trim leading and trailing spaces
         Date = sub(" *$", "", Date),         # Remove spaces at the end
         Date = gsub(" ", "-", Date))         # Replace remaining spaces with "-"
```

```{r}
# date split df
df_date <- data.frame(stringr::str_split_fixed(df23$Date, '-', n = 3))
colnames(df_date) <- c('Date_day', 'Date_month', 'Date_year')

# add to df column
df23 <- cbind(df23, df_date)
```

```{r}
df23 <- df23 %>%
  # formatting the date column
  mutate(Date = case_when(.default = paste0(Date_day, '-',  Date_month, '-', Date_year),
                          Date_month == 'Sept' ~ paste0(Date_day, '-Sep-', Date_year))) %>%
  mutate(Date = as.Date(Date, format = "%d-%b-%Y"), Year = Date_year) %>%
  # standardizing names and making a full name column
  mutate(LastName = toupper(LastName), FirstName = toupper(FirstName), 
         FullName = paste0(LastName, ' ', FirstName), 
         Date = as.Date(Date, format = "%d-%b-%Y")) %>%
  select(-Date_year, -Date_month, -Date_day, -LastName, -FirstName)
```

```{r}
# saving full dataframe
write.csv(df23, "cleaned data/full_data_2023.csv")
```



## Main graph (Women)

You only need to run this to make the graph

```{r}
library(ggpubr)
```

```{r adding round type and stage to women data - EDA by round}
women <- read.csv("cleaned data/active_restricted_women_2023.csv")
women <- women %>%
  mutate(Round = tolower(Round),
         RoundStage = case_when(stringr::str_like(Round,'%final%') ~ "final",
                           stringr::str_like(Round,'%qual%') ~ "qual"),
         RoundType = case_when(stringr::str_like(Round,'%team%') ~ "team",
                           stringr::str_like(Round,'%aa%') ~ "all around",
                           .default = "individual"))
```

*getting data for graphs*
```{r getting top 3 women for vt - EDA by round}
top_vt_women_names <- women %>%
  filter(stringr::str_like(Apparatus,'VT%')) %>%
  group_by(FullName) %>%
  summarise(avg_score = mean(Score, na.rm = T)) %>%
  ungroup () %>%
  arrange(desc(avg_score)) %>%
  distinct(FullName, .keep_all = T) %>%
  slice(1:3) %>%
  pull(FullName)

top_vt_women_avg <- women %>%
  filter(stringr::str_like(Apparatus,'VT%')) %>%
  filter(FullName %in% top_vt_women_names) %>%
  group_by(FullName, Round, RoundType, RoundStage, Country) %>%
  summarise(avg_score = round(mean(Score, na.rm = T), 1)) %>%
  ungroup() %>%
  arrange(desc(avg_score))
```

```{r getting top 3 women for bb - EDA by round}
top_bb_women_names <- women %>%
  filter(stringr::str_like(Apparatus,'BB%')) %>%
  group_by(FullName) %>%
  summarise(avg_score = mean(Score, na.rm = T)) %>%
  ungroup () %>%
  arrange(desc(avg_score)) %>%
  distinct(FullName, .keep_all = T) %>%
  slice(1:3) %>%
  pull(FullName)

top_bb_women_avg <- women %>%
  filter(stringr::str_like(Apparatus,'BB%')) %>%
  filter(FullName %in% top_bb_women_names) %>%
  group_by(FullName, Round, RoundType, RoundStage, Country) %>%
  summarise(avg_score = round(mean(Score, na.rm = T), 1)) %>%
  ungroup() %>%
  arrange(desc(avg_score))
```

```{r getting top 3 women for ub - EDA by round}
top_ub_women_names <- women %>%
  filter(stringr::str_like(Apparatus,'UB%')) %>%
  group_by(FullName) %>%
  summarise(avg_score = mean(Score, na.rm = T)) %>%
  ungroup () %>%
  arrange(desc(avg_score)) %>%
  distinct(FullName, .keep_all = T) %>%
  slice(1:3) %>%
  pull(FullName)

top_ub_women_avg <- women %>%
  filter(stringr::str_like(Apparatus,'UB%')) %>%
  filter(FullName %in% top_ub_women_names) %>%
  group_by(FullName, Round, RoundType, RoundStage, Country) %>%
  summarise(avg_score = round(mean(Score, na.rm = T), 1)) %>%
  ungroup() %>%
  arrange(desc(avg_score))
```

```{r getting top 3 women for fx - EDA by round}
top_fx_women_names <- women %>%
  filter(stringr::str_like(Apparatus,'FX%')) %>%
  group_by(FullName) %>%
  summarise(avg_score = mean(Score, na.rm = T)) %>%
  ungroup () %>%
  arrange(desc(avg_score)) %>%
  distinct(FullName, .keep_all = T) %>%
  slice(1:3) %>%
  pull(FullName)

top_fx_women_avg <- women %>%
  filter(stringr::str_like(Apparatus,'FX%')) %>%
  filter(FullName %in% top_fx_women_names) %>%
  group_by(FullName, Round, RoundType, RoundStage, Country) %>%
  summarise(avg_score = round(mean(Score, na.rm = T), 1)) %>%
  ungroup() %>%
  arrange(desc(avg_score))
```

```{r making graphs for EDA by round}
pvt <- ggplot(top_vt_women_avg, mapping = aes(x = avg_score, y = FullName, fill = Country)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=avg_score), size = 3.5,  hjust = 1.1) +
  facet_nested_wrap(~RoundStage + RoundType, nrow = 1) +
  labs(title = "Average Women's Vault Scores by Round", 
       subtitle = "For the Top 3 Athletes by Overall Average Vault Score",
       x = "Average Score by Round", y = "")

pbb <- ggplot(top_bb_women_avg, mapping = aes(x = avg_score, y = FullName, fill = Country)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=avg_score), size = 3.5,  hjust = 1.1) +
  facet_nested_wrap(~RoundStage + RoundType, nrow = 1) +
  labs(title = "Average Women's Balance Beam Scores by Round", 
       subtitle = "For the Top 3 Athletes by Overall Average Balance Beam Score",
       x = "Average Score by Round", y = "")

pub <- ggplot(top_ub_women_avg, mapping = aes(x = avg_score, y = FullName, fill = Country)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=avg_score), size = 3.5,  hjust = 1.1) +
  facet_nested_wrap(~RoundStage + RoundType, nrow = 1) +
  labs(title = "Average Women's Uneven Bar Scores by Round", 
       subtitle = "For the Top 3 Athletes by Overall Average Uneven Bar Score",
       x = "Average Score by Round", y = "")

pfx <- ggplot(top_fx_women_avg, mapping = aes(x = avg_score, y = FullName, fill = Country)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=avg_score), size = 3.5,  hjust = 1.1) +
  facet_nested_wrap(~RoundStage + RoundType, nrow = 1) +
  labs(title = "Average Women's Floor Scores by Round", 
       subtitle = "For the Top 3 Athletes by Overall Average Floor Score",
       x = "Average Score by Round", y = "")
```


```{r fig.width = 15}
ggarrange(pvt, pbb, pub, pfx)
```

## Main graph (MEN)

You only need to run this part to make the graph

```{r getting active restricted df for men}
men <- read.csv("cleaned data/active_restricted_men_2023.csv")
```


```{r adding round type and round stage for men}
# adding round stage and type
men <- men %>%
  mutate(Round = tolower(Round),
         RoundStage = case_when(stringr::str_like(Round,'%final%') ~ "final",
                           stringr::str_like(Round,'%qual%') ~ "qual"),
         RoundType = case_when(stringr::str_like(Round,'%team%') ~ "team",
                           stringr::str_like(Round,'%aa%') ~ "all around",
                           .default = "individual"))
```

*getting data for graphs*
```{r getting top 3 men for HB - EDA by round}
top_hb_men_names <- men %>%
  filter(stringr::str_like(Apparatus,'HB%')) %>%
  group_by(FullName) %>%
  summarise(avg_score = mean(Score, na.rm = T)) %>%
  ungroup () %>%
  arrange(desc(avg_score)) %>%
  distinct(FullName, .keep_all = T) %>%
  slice(1:3) %>% 
  pull(FullName)

top_hb_men_avg <- men %>%
  filter(FullName %in% top_hb_men_names) %>%
  group_by(FullName, Round, RoundType, RoundStage, Country) %>%
  summarise(avg_score = round(mean(Score, na.rm = T), 1)) %>%
  ungroup() %>%
  arrange(desc(avg_score))
```

```{r getting top 3 men for PH - EDA by round}
top_ph_men_names <- men %>%
  filter(stringr::str_like(Apparatus,'PH%')) %>%
  group_by(FullName) %>%
  summarise(avg_score = mean(Score, na.rm = T)) %>%
  ungroup () %>%
  arrange(desc(avg_score)) %>%
  distinct(FullName, .keep_all = T) %>%
  slice(1:3) %>% 
  pull(FullName)

top_ph_men_avg <- men %>%
  filter(stringr::str_like(Apparatus,'PH%')) %>%
  filter(FullName %in% top_ph_men_names) %>%
  group_by(FullName, Round, RoundType, RoundStage, Country) %>%
  summarise(avg_score = round(mean(Score, na.rm = T), 1)) %>%
  ungroup() %>%
  arrange(desc(avg_score))
```

```{r getting top 3 men for SR - EDA by round}
top_sr_men_names <- men %>%
  filter(stringr::str_like(Apparatus,'SR%')) %>%
  group_by(FullName) %>%
  summarise(avg_score = mean(Score, na.rm = T)) %>%
  ungroup () %>%
  arrange(desc(avg_score)) %>%
  distinct(FullName, .keep_all = T) %>%
  slice(1:3) %>% 
  pull(FullName)

top_sr_men_avg <- men %>%
  filter(stringr::str_like(Apparatus,'SR%')) %>%
  filter(FullName %in% top_sr_men_names) %>%
  group_by(FullName, Round, RoundType, RoundStage, Country) %>%
  summarise(avg_score = round(mean(Score, na.rm = T), 1)) %>%
  ungroup() %>%
  arrange(desc(avg_score))
```

```{r getting top 3 men for FX - EDA by round}
top_fx_men_names <- men %>%
  filter(stringr::str_like(Apparatus,'FX%')) %>%
  group_by(FullName) %>%
  summarise(avg_score = mean(Score, na.rm = T)) %>%
  ungroup () %>%
  arrange(desc(avg_score)) %>%
  distinct(FullName, .keep_all = T) %>%
  slice(1:3) %>% 
  pull(FullName)

top_fx_men_avg <- men %>%
  filter(stringr::str_like(Apparatus,'FX%')) %>%
  filter(FullName %in% top_fx_men_names) %>%
  group_by(FullName, Round, RoundType, RoundStage, Country) %>%
  summarise(avg_score = round(mean(Score, na.rm = T), 1)) %>%
  ungroup() %>%
  arrange(desc(avg_score))
```

```{r getting top 3 men for VT - EDA by round}
top_vt_men_names <- men %>%
  filter(stringr::str_like(Apparatus,'VT%')) %>%
  group_by(FullName) %>%
  summarise(avg_score = mean(Score, na.rm = T)) %>%
  ungroup () %>%
  arrange(desc(avg_score)) %>%
  distinct(FullName, .keep_all = T) %>%
  slice(1:3) %>% 
  pull(FullName)

top_vt_men_avg <- men %>%
  filter(stringr::str_like(Apparatus,'VT%')) %>%
  filter(FullName %in% top_vt_men_names) %>%
  group_by(FullName, Round, RoundType, RoundStage, Country) %>%
  summarise(avg_score = round(mean(Score, na.rm = T), 1)) %>%
  ungroup() %>%
  arrange(desc(avg_score))
```

```{r getting top 3 men for PB - EDA by round}
top_pb_men_names <- men %>%
  filter(stringr::str_like(Apparatus,'PB%')) %>%
  group_by(FullName) %>%
  summarise(avg_score = mean(Score, na.rm = T)) %>%
  ungroup () %>%
  arrange(desc(avg_score)) %>%
  distinct(FullName, .keep_all = T) %>%
  slice(1:3) %>% 
  pull(FullName)

top_pb_men_avg <- men %>%
  filter(stringr::str_like(Apparatus,'PB%')) %>%
  filter(FullName %in% top_pb_men_names) %>%
  group_by(FullName, Round, RoundType, RoundStage, Country) %>%
  summarise(avg_score = round(mean(Score, na.rm = T), 1)) %>%
  ungroup() %>%
  arrange(desc(avg_score))
```

```{r getting top 3 men for VT - EDA by round}
top_vt_men_names <- men %>%
  filter(stringr::str_like(Apparatus,'VT%')) %>%
  group_by(FullName) %>%
  summarise(avg_score = mean(Score, na.rm = T)) %>%
  ungroup () %>%
  arrange(desc(avg_score)) %>%
  distinct(FullName, .keep_all = T) %>%
  slice(1:3) %>% 
  pull(FullName)

top_vt_men_avg <- men %>%
  filter(stringr::str_like(Apparatus,'VT%')) %>%
  filter(FullName %in% top_vt_men_names) %>%
  group_by(FullName, Round, RoundType, RoundStage, Country) %>%
  summarise(avg_score = round(mean(Score, na.rm = T), 1)) %>%
  ungroup() %>%
  arrange(desc(avg_score))
```

```{r getting all graphs - EDA by round}
pvt <- ggplot(top_vt_men_avg, mapping = aes(x = avg_score, y = FullName, fill = Country)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=avg_score), size = 3.5,  hjust = 1.1) +
  facet_nested_wrap(~RoundStage + RoundType, nrow = 1) +
  labs(title = "Average Men's Vault Scores by Round", 
       subtitle = "For the Top 3 Athletes by Overall Average Vault Score",
       x = "Average Score by Round", y = "")

pph <- ggplot(top_ph_men_avg, mapping = aes(x = avg_score, y = FullName, fill = Country)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=avg_score), size = 3.5,  hjust = 1.1) +
  facet_nested_wrap(~RoundStage + RoundType, nrow = 1) +
  labs(title = "Average Men's Pommel Horse Scores by Round", 
       subtitle = "For the Top 3 Athletes by Overall Average Pommel Horse Score",
       x = "Average Score by Round", y = "")

psr <- ggplot(top_sr_men_avg, mapping = aes(x = avg_score, y = FullName, fill = Country)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=avg_score), size = 3.5,  hjust = 1.1) +
  facet_nested_wrap(~RoundStage + RoundType, nrow = 1) +
  labs(title = "Average Men's Still Rings Scores by Round", 
       subtitle = "For the Top 3 Athletes by Overall Average Still Rings Score",
       x = "Average Score by Round", y = "")

pfx <- ggplot(top_fx_men_avg, mapping = aes(x = avg_score, y = FullName, fill = Country)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=avg_score), size = 3.5,  hjust = 1.1) +
  facet_nested_wrap(~RoundStage + RoundType, nrow = 1) +
  labs(title = "Average Men's Floor Scores by Round", 
       subtitle = "For the Top 3 Athletes by Overall Average Floor Score",
       x = "Average Score by Round", y = "")

ppb <- ggplot(top_pb_men_avg, mapping = aes(x = avg_score, y = FullName, fill = Country)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=avg_score), size = 3.5,  hjust = 1.1) +
  facet_nested_wrap(~RoundStage + RoundType, nrow = 1) +
  labs(title = "Average Men's Parallel Bars Scores by Round", 
       subtitle = "For the Top 3 Athletes by Overall Average Parallel Bars Score",
       x = "Average Score by Round", y = "")

phb <- ggplot(top_hb_men_avg, mapping = aes(x = avg_score, y = FullName, fill = Country)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=avg_score), size = 3.5,  hjust = 1.1) +
  facet_nested_wrap(~RoundStage + RoundType, nrow = 1) +
  labs(title = "Average Men's Horizontal Bar Scores by Round", 
       subtitle = "For the Top 3 Athletes by Overall Average Horizontal Bar Score",
       x = "Average Score by Round", y = "")
```


```{r fig.width = 20 EDA by round}
ggarrange(pvt, pph, phb, ppb, psr, pfx)
```


## Loading Data and Data Cleaning 

```{r}
df <- read.csv("cleaned data/data_2022_2023_cleaned.csv")
df_old <- read.csv("data/data_2017_2021.csv")
```


### Old Data
```{r}
# all of this data is from the 2021 Olympics
df_old %>%
  filter(Competition != "Olympic Games")
```

```{r}
# only has women
df_old %>%
  filter(Gender != 'w')
```


```{r}
df_old <- df_old %>%
  # removing day of the week and the Julys
  mutate(Date = case_when(is.na(as.numeric(substr(Date, 1, 1))) ~ substr(Date, 4, 15),
                          .default = substr(Date, 1, 15)),
         Date = toupper(Date),
         Date = case_when(.default = substr(Date, 1, 15),
                          substr(substr(Date, 4, 8), 4,4) == 'Y' ~ paste(substr(Date, 1,2), 'JUL', substr(Date, 8, 15))))
         
```

```{r}
# no NAs
sum(is.na(df_old$Date))
```


```{r}
# changing to date format 
df_old <- df_old %>%
  mutate(Date = as.Date(Date, format = "%d %b %Y"))
```


### Most Recent Data

```{r}
# date split df
df_date <- data.frame(stringr::str_split_fixed(df$Date, '-', n = 3))
colnames(df_date) <- c('Date_day', 'Date_month', 'Date_year')

# add to df column
df <- cbind(df, df_date)
```

```{r}
df <- df %>%
  # formatting the date column
  mutate(Date = case_when(.default = paste0(Date_day, '-',  Date_month, '-', Date_year),
                          Date_month == 'Sept' ~ paste0(Date_day, '-Sep-', Date_year))) %>%
  mutate(Date = as.Date(Date, format = "%d-%b-%Y"), Year = Date_year) %>%
  # standardizing names and making a full name column
  mutate(LastName = toupper(LastName), FirstName = toupper(FirstName), 
         FullName = paste0(LastName, ' ', FirstName), 
         Date = as.Date(Date, format = "%d-%b-%Y")) %>%
  select(-Date_year, -Date_month, -Date_day, -LastName, -FirstName)
```

```{r}
# vt1 and VT2 have a lot of NAs
# 33 NAs are from Croatia, GBR has 17 and PAN has 13
# 50 nas come from last year's world championships 
df %>%
  filter(is.na(Score)) %>%
  group_by(Competition) %>%
  count() %>%
  arrange(desc(n))
```


## Filtering USA Data

```{r}
df_usa <- df %>%
  filter(Country == 'USA')

df_old_usa <- df_old %>%
  filter(Country == 'USA')
```


```{r}
# competitions 
df_usa %>%
  select(Competition) %>%
  distinct()
```

```{r}
# athletes represented 
df_usa %>%
  select(FullName) %>%
  distinct()
```

```{r}
# athletes in the 2021 olympics
df_old_usa %>%
  select(LastName) %>%
  distinct()
```


## Loading active restricted data

```{r}
men <- read.csv("cleaned data/active_restricted_men_2023.csv")
women <- read.csv("cleaned data/active_restricted_women_2023.csv")
```


## Scoring Trends for Female US Athletes

```{r}
# making data frame
df_usaw <- df_usa[df_usa['Gender'] == 'w',]
```

```{r}
df_usaw %>%
  select(FullName) %>%
  distinct()
```

### Relationship among AA scores

```{r}
df_usaw %>%
  select(FullName, Competition, Round, Score) %>%
  filter(Round == 'AAfinal')
```



### Relationship among apparatuses by athlete

```{r}
# checking best scores across all comps
df_usaw_scores <- df_usaw[,c('FullName', 'Apparatus', 'Score')] %>%
  arrange(desc(Score)) %>%
  distinct(FullName, Apparatus, .keep_all = TRUE) %>%
  pivot_wider(names_from = Apparatus, values_from = Score)

head(df_usaw_scores)
```


```{r}
# some high correlations, especially for vault, balance beam, and floor exercises (all positive)
# uneven bars are the exception 
cor(df_usaw_scores[,c('VT', 'VT1', 'VT2', 'UB', 'BB', 'FX')], use = "complete.obs")
```

```{r}
# outlier in UB
ggplot(df_usaw_scores, aes(x = VT, y = UB)) +
  geom_point()
```

### Are All-Around Scores correlated?
Idk how to check
```{r}
 df_usaw %>%
  select('FullName', 'Competition', 'Round', 'Score') %>%
  filter(Round == 'AAfinal') %>%
  arrange(Competition)
```


```{r}
women <- women %>%
  mutate(Round = tolower(Round),
         RoundStage = case_when(stringr::str_like(Round,'%final%') ~ "final",
                           stringr::str_like(Round,'%qual%') ~ "qual"),
         RoundType = case_when(stringr::str_like(Round,'%team%') ~ "team",
                           stringr::str_like(Round,'%aa%') ~ "all around",
                           .default = "individual"))
```

```{r}
women %>%
  distinct(RoundType)
```


### Vault

```{r}
# looking at score range 
vt_women <- women %>%
  filter(stringr::str_like(Apparatus,'VT%'))

vt_women %>%
  select(FullName, Round, RoundType, Score)
```

```{r}
summary(aov(Score ~ FullName + RoundStage + RoundType + FullName*RoundType + FullName*RoundStage + RoundStage*RoundType, data = vt_women))
```

```{r}
top3_vt_women_names <- vt_women %>%
  group_by(FullName) %>%
  summarise(avg_score = mean(Score, na.rm = T)) %>%
  ungroup () %>%
  arrange(desc(avg_score)) %>%
  distinct(FullName, .keep_all = T) %>%
  slice(1:3) %>%
  pull(FullName)
```

```{r}
top_vt_women_avg <- vt_women %>%
  filter(FullName %in% top3_vt_women_names) %>%
  group_by(FullName, Round, RoundType, RoundStage, Country) %>%
  summarise(avg_score = round(mean(Score, na.rm = T), 1)) %>%
  ungroup() %>%
  arrange(desc(avg_score))
```



```{r}
pvt <- ggplot(top_vt_women_avg, mapping = aes(x = avg_score, y = FullName, fill = Country)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=avg_score), size = 3.5,  hjust = 1.1) +
  facet_nested_wrap(~RoundStage + RoundType, nrow = 1) +
  labs(title = "Average Women's Vault Scores by Round", 
       subtitle = "For the Top 3 Athletes by Overall Average Vault Score",
       x = "Average Score by Round", y = "")
```




### Balance Beam

```{r}
# looking at score range 
bb_women <- women %>%
  filter(stringr::str_like(Apparatus,'BB%'))

bb_women %>%
  select(FullName, Round, RoundStage, RoundType, Score)
```

```{r}
summary(aov(Score ~ FullName + RoundStage + RoundType + FullName*RoundType + FullName*RoundStage + RoundStage*RoundType, data = bb_women))
```

```{r}
top5_bb_women_names <- bb_women %>%
  group_by(FullName) %>%
  summarise(avg_score = mean(Score, na.rm = T)) %>%
  ungroup () %>%
  arrange(desc(avg_score)) %>%
  distinct(FullName, .keep_all = T) %>%
  slice(1:3) %>%
  pull(FullName)
```

```{r}
top_bb_women_avg <- bb_women %>%
  filter(FullName %in% top5_bb_women_names) %>%
  group_by(FullName, Round, RoundStage, RoundType, Country) %>%
  summarise(avg_score = round(mean(Score, na.rm = T), 1)) %>%
  ungroup() %>%
  arrange(desc(avg_score))
```

```{r}
pbb <- ggplot(top_bb_women_avg, mapping = aes(x = avg_score, y = FullName, fill = Country)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=avg_score), size = 3.5,  hjust = 1.1) +
  facet_nested_wrap(~RoundStage + RoundType, nrow = 1) +
  labs(title = "Average Women's Balance Beam Scores by Round", 
       subtitle = "For the Top 3 Athletes by Overall Average Balance Beam Score",
       x = "Average Score by Round", y = "")
```


### Uneven Bars

```{r}
# looking at score range 
ub_women <- women %>%
  filter(stringr::str_like(Apparatus,'UB%'))

ub_women %>%
  select(FullName, Round, RoundStage, RoundType, Score)
```

```{r}
summary(aov(Score ~ FullName + RoundStage + RoundType + FullName*RoundType + FullName*RoundStage + RoundStage*RoundType, data = ub_women))
```

```{r}
top5_ub_women_names <- ub_women %>%
  group_by(FullName) %>%
  summarise(avg_score = mean(Score, na.rm = T)) %>%
  ungroup () %>%
  arrange(desc(avg_score)) %>%
  distinct(FullName, .keep_all = T) %>%
  slice(1:3) %>%
  pull(FullName)
```

```{r}
top_ub_women_avg <- ub_women %>%
  filter(FullName %in% top5_ub_women_names) %>%
  group_by(FullName, Round, RoundStage, RoundType, Country) %>%
  summarise(avg_score = round(mean(Score, na.rm = T), 1)) %>%
  ungroup() %>%
  arrange(desc(avg_score))
```

```{r}
pub <- ggplot(top_ub_women_avg, mapping = aes(x = avg_score, y = FullName, fill = Country)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=avg_score), size = 3.5,  hjust = 1.1) +
  facet_nested_wrap(~RoundStage + RoundType, nrow = 1) +
  labs(title = "Average Women's Uneven Bar Scores by Round", 
       subtitle = "For the Top 3 Athletes by Overall Average Uneven Bar Score",
       x = "Average Score by Round", y = "")
```

### Floor Exercise

```{r}
# looking at score range 
fx_women <- women %>%
  filter(stringr::str_like(Apparatus,'FX%'))

fx_women %>%
  select(FullName, Round, RoundStage, RoundType, Score)
```

```{r}
summary(aov(Score ~ FullName + RoundStage + RoundType + FullName*RoundType + FullName*RoundStage + RoundStage*RoundType, data = fx_women))
```

```{r}
top5_fx_women_names <- fx_women %>%
  group_by(FullName) %>%
  summarise(avg_score = mean(Score, na.rm = T)) %>%
  ungroup () %>%
  arrange(desc(avg_score)) %>%
  distinct(FullName, .keep_all = T) %>%
  slice(1:3) %>%
  pull(FullName)
```

```{r}
top_fx_women_avg <- fx_women %>%
  filter(FullName %in% top5_fx_women_names) %>%
  group_by(FullName, Round, RoundStage, RoundType, Country) %>%
  summarise(avg_score = round(mean(Score, na.rm = T), 1)) %>%
  ungroup() %>%
  arrange(desc(avg_score))
```

```{r}
pfx <- ggplot(top_fx_women_avg, mapping = aes(x = avg_score, y = FullName, fill = Country)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=avg_score), size = 3.5,  hjust = 1.1) +
  facet_nested_wrap(~RoundStage + RoundType, nrow = 1) +
  labs(title = "Average Women's Floor Scores by Round", 
       subtitle = "For the Top 3 Athletes by Overall Average Floor Score",
       x = "Average Score by Round", y = "")
```





## Men

```{r}
men <- 
```


```{r }
men <- men %>%
  mutate(Round = tolower(Round),
         RoundStage = case_when(stringr::str_like(Round,'%final%') ~ "final",
                           stringr::str_like(Round,'%qual%') ~ "qual"),
         RoundType = case_when(stringr::str_like(Round,'%team%') ~ "team",
                           stringr::str_like(Round,'%aa%') ~ "all around",
                           .default = "individual"))
```


### Vault

```{r}
# looking at score range 
vt_men <- men %>%
  filter(stringr::str_like(Apparatus,'VT%'))

vt_men %>%
  select(FullName, Round, RoundStage, RoundType, Score)
```

```{r}
summary(aov(Score ~ FullName + RoundStage + RoundType + FullName*RoundType + FullName*RoundStage + RoundStage*RoundType, data = vt_men))
```

```{r}
top3_vt_men_names <- vt_men %>%
  group_by(FullName) %>%
  summarise(avg_score = mean(Score, na.rm = T)) %>%
  ungroup () %>%
  arrange(desc(avg_score)) %>%
  distinct(FullName, .keep_all = T) %>%
  slice(1:3) %>%
  pull(FullName)
```

```{r}
top_vt_men_avg <- vt_men %>%
  filter(FullName %in% top3_vt_men_names) %>%
  group_by(FullName, Round, RoundType, RoundStage, Country) %>%
  summarise(avg_score = round(mean(Score, na.rm = T), 1)) %>%
  ungroup() %>%
  arrange(desc(avg_score))
```



```{r}
pvt <- ggplot(top_vt_men_avg, mapping = aes(x = avg_score, y = FullName, fill = Country)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=avg_score), size = 3.5,  hjust = 1.1) +
  facet_nested_wrap(~RoundStage + RoundType, nrow = 1) +
  labs(title = "Average Men's Vault Scores by Round", 
       subtitle = "For the Top 3 Athletes by Overall Average Vault Score",
       x = "Average Score by Round", y = "")
```

```{r}
pvt
```


### Pommel Horse

```{r}
# looking at score range 
ph_men <- men %>%
  filter(stringr::str_like(Apparatus,'PH%'))

ph_men %>%
  select(FullName, Apparatus, Round, RoundStage, RoundType, Score)
```

```{r}
summary(aov(Score ~ FullName + RoundStage + RoundType + FullName*RoundType + FullName*RoundStage + RoundStage*RoundType, data = ph_men))
```

```{r}
top3_ph_men_names <- ph_men %>%
  group_by(FullName) %>%
  summarise(avg_score = mean(Score, na.rm = T)) %>%
  ungroup () %>%
  arrange(desc(avg_score)) %>%
  distinct(FullName, .keep_all = T) %>%
  slice(1:3) %>%
  pull(FullName)
```

```{r}
top_ph_men_avg <- ph_men %>%
  filter(FullName %in% top3_ph_men_names) %>%
  group_by(FullName, Round, RoundType, RoundStage, Country) %>%
  summarise(avg_score = round(mean(Score, na.rm = T), 1)) %>%
  ungroup() %>%
  arrange(desc(avg_score))
```



```{r}
pph <- ggplot(top_ph_men_avg, mapping = aes(x = avg_score, y = FullName, fill = Country)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=avg_score), size = 3.5,  hjust = 1.1) +
  facet_nested_wrap(~RoundStage + RoundType, nrow = 1) +
  labs(title = "Average Men's Pommel Horse Scores by Round", 
       subtitle = "For the Top 3 Athletes by Overall Average Pommel Horse Score",
       x = "Average Score by Round", y = "")
```

```{r}
pph
```

### Still Rings

```{r}
# looking at score range 
sr_men <- men %>%
  filter(stringr::str_like(Apparatus,'SR%'))

sr_men %>%
  select(FullName, Apparatus, Round, RoundStage, RoundType, Score)
```

```{r}
summary(aov(Score ~ FullName + RoundStage + RoundType + FullName*RoundType + FullName*RoundStage + RoundStage*RoundType, data = sr_men))
```

```{r}
top3_sr_men_names <- sr_men %>%
  group_by(FullName) %>%
  summarise(avg_score = mean(Score, na.rm = T)) %>%
  ungroup () %>%
  arrange(desc(avg_score)) %>%
  distinct(FullName, .keep_all = T) %>%
  slice(1:3) %>%
  pull(FullName)
```

```{r}
top_sr_men_avg <- sr_men %>%
  filter(FullName %in% top3_sr_men_names) %>%
  group_by(FullName, Round, RoundType, RoundStage, Country) %>%
  summarise(avg_score = round(mean(Score, na.rm = T), 1)) %>%
  ungroup() %>%
  arrange(desc(avg_score))
```



```{r}
psr <- ggplot(top_sr_men_avg, mapping = aes(x = avg_score, y = FullName, fill = Country)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=avg_score), size = 3.5,  hjust = 1.1) +
  facet_nested_wrap(~RoundStage + RoundType, nrow = 1) +
  labs(title = "Average Men's Still Rings Scores by Round", 
       subtitle = "For the Top 3 Athletes by Overall Average Still Rings Score",
       x = "Average Score by Round", y = "")
```

```{r}
psr
```


### Floor

```{r}
# looking at score range 
fx_men <- men %>%
  filter(stringr::str_like(Apparatus,'FX%'))

fx_men %>%
  select(FullName, Apparatus, Round, RoundStage, RoundType, Score)
```

```{r}
summary(aov(Score ~ FullName + RoundStage + RoundType + FullName*RoundType + FullName*RoundStage + RoundStage*RoundType, data = fx_men))
```

```{r}
top3_fx_men_names <- fx_men %>%
  group_by(FullName) %>%
  summarise(avg_score = mean(Score, na.rm = T)) %>%
  ungroup () %>%
  arrange(desc(avg_score)) %>%
  distinct(FullName, .keep_all = T) %>%
  slice(1:3) %>%
  pull(FullName)
```

```{r}
top_fx_men_avg <- fx_men %>%
  filter(FullName %in% top3_fx_men_names) %>%
  group_by(FullName, Round, RoundType, RoundStage, Country) %>%
  summarise(avg_score = round(mean(Score, na.rm = T), 1)) %>%
  ungroup() %>%
  arrange(desc(avg_score))
```



```{r}
pfx <- ggplot(top_fx_men_avg, mapping = aes(x = avg_score, y = FullName, fill = Country)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=avg_score), size = 3.5,  hjust = 1.1) +
  facet_nested_wrap(~RoundStage + RoundType, nrow = 1) +
  labs(title = "Average Men's Floor Scores by Round", 
       subtitle = "For the Top 3 Athletes by Overall Average Floor Score",
       x = "Average Score by Round", y = "")
```

```{r}
pfx
```



### Parallel Bars

```{r}
# looking at score range 
pb_men <- men %>%
  filter(stringr::str_like(Apparatus,'PB%'))

pb_men %>%
  select(FullName, Apparatus, Round, RoundStage, RoundType, Score)
```

```{r}
summary(aov(Score ~ FullName + RoundStage + RoundType + FullName*RoundType + FullName*RoundStage + RoundStage*RoundType, data = pb_men))
```

```{r}
top3_pb_men_names <- pb_men %>%
  group_by(FullName) %>%
  summarise(avg_score = mean(Score, na.rm = T)) %>%
  ungroup () %>%
  arrange(desc(avg_score)) %>%
  distinct(FullName, .keep_all = T) %>%
  slice(1:3) %>%
  pull(FullName)
```

```{r}
top_pb_men_avg <- pb_men %>%
  filter(FullName %in% top3_pb_men_names) %>%
  group_by(FullName, Round, RoundType, RoundStage, Country) %>%
  summarise(avg_score = round(mean(Score, na.rm = T), 1)) %>%
  ungroup() %>%
  arrange(desc(avg_score))
```



```{r}
ppb <- ggplot(top_pb_men_avg, mapping = aes(x = avg_score, y = FullName, fill = Country)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=avg_score), size = 3.5,  hjust = 1.1) +
  facet_nested_wrap(~RoundStage + RoundType, nrow = 1) +
  labs(title = "Average Men's Parallel Bars Scores by Round", 
       subtitle = "For the Top 3 Athletes by Overall Average Parallel Bars Score",
       x = "Average Score by Round", y = "")
```

```{r}
ppb
```


### Horizontal Bars


```{r}
# looking at score range 
hb_men <- men %>%
  filter(stringr::str_like(Apparatus,'HB%'))

hb_men %>%
  select(FullName, Apparatus, Round, RoundStage, RoundType, Score)
```

```{r}
summary(aov(Score ~ FullName + RoundStage + RoundType + FullName*RoundType + FullName*RoundStage + RoundStage*RoundType, data = hb_men))
```

```{r}
top3_hb_men_names <- hb_men %>%
  group_by(FullName) %>%
  summarise(avg_score = mean(Score, na.rm = T)) %>%
  ungroup () %>%
  arrange(desc(avg_score)) %>%
  distinct(FullName, .keep_all = T) %>%
  slice(1:3) %>%
  pull(FullName)
```

```{r}
top_hb_men_avg <- hb_men %>%
  filter(FullName %in% top3_hb_men_names) %>%
  group_by(FullName, Round, RoundType, RoundStage, Country) %>%
  summarise(avg_score = round(mean(Score, na.rm = T), 1)) %>%
  ungroup() %>%
  arrange(desc(avg_score))
```



```{r}
phb <- ggplot(top_hb_men_avg, mapping = aes(x = avg_score, y = FullName, fill = Country)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label=avg_score), size = 3.5,  hjust = 1.1) +
  facet_nested_wrap(~RoundStage + RoundType, nrow = 1) +
  labs(title = "Average Men's Horizontal Bar Scores by Round", 
       subtitle = "For the Top 3 Athletes by Overall Average Horizontal Bar Score",
       x = "Average Score by Round", y = "")
```

```{r}
phb
```








