---
title: "Creating Smaller Dataset and EDA"
author: "Elyse McFalls"
date: "2023-11-09"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```


## Loading full data

```{r}
df_full <- read.csv("cleaned data/full_data_2023.csv")
head(df_full)
```

## Selecting Olympic Bound Countries and Individuals

### Men:

[link](https://www.gymnastics.sport/site/news/displaynews.php?urlNews=3989229#:~:text=The%20Paris%202024%20Olympic%20team%20tableau%20is,decide%20the%20destination%20of%20the%20Olympic%20medals)
- USA
- Canada
- Germany
- Italy
- Switzerland
- Spain
- Turkey
- the Netherlands
- Ukraine
- the People's Republic of China
- Japan
- Great Britain
- Brazil (1 person)
- the Republic of Korea (1 person)
- Belguim (1 person)

Individuals:
- Milad Karimi (indv.)
- Artem Dolgopyat (indv.)
- Artur Davtyan (indv.)
- Krisztofer Meszaros (indv.)
- Lee Junho (KOR)
- Soares, Luca van den Keybus (indv.)
- Andrei Muntean (indv.)

```{r}
df_full_men_teams <- df_full %>%
  filter(Gender == 'm' &
         Country %in% c('USA', 'CAN', 'GER', 'ITA', 'SUI', 'ESP', 'TUR', 'NED', 
                        'UKR', 'CHN', 'JPN', 'GBR', 'BRA', 'KOR', 'BEL')) 
```

```{r}
# Juhno lee is in the data twice, one as Junho Lee and one as Lee Junho
# same for Soares, Luca van den Keybus from Belgium 
# the other ones are fine
df_men_indv <- df_full %>%
  filter(FullName %in% c("KARIMI MILAD", "DOLGOPYAT ARTEM", "DAVTYAN ARTUR",
                           "MESZAROS KRISZTOFER", "MUNTEAN ANDREI", "LEE JUHNO", 
                          "JUHNO LEE", "KEYBUS LUKA", "VAN LUKA"))
```


```{r}
# break off criteria: athletes that have ranked at least top for all countries
df_men_names <- df_full_men_teams %>%
  filter(Rank <= 5) %>%
  distinct(FullName) %>%
  pull()

df_men <- df_full_men_teams %>%
  filter(FullName %in% df_men_names)
```


```{r}
# adding individuals, using distinct incase of overlap 
df_men <- rbind(df_men, df_men_indv) %>%
  distinct(.keep_all = T)
```

```{r}
# writing to csv
write_csv(df_men, "cleaned data/restricted_men_2023.csv")
```

```{r}
df_men
```

```{r}
df_men %>%
  distinct(FullName)
```


### Women:
[link](https://www.insidethegames.biz/articles/1141357/artistic-gymnastics-paris-2024-places) 
- USA
- Great Britain
- Canada
- the People's Republic of China
- Brazil 
- Italy
- the Netherlands
- France
- Japan
- Australia
- Romania
- the Republic of Korea 
- Germany (1 person)
- Mexico (1 person)
- Hungary (1 person)

- Individuals:
  - Kaylia Nemour (ALG)
  -Pauline Schaefer-Betz (GER)
  - Alexa Moreno (MEX)
  - Filipa Martins (POR)
  - Aleah Finnegan (PHI)
  - Bettina Lili Czifra (HUN)
  - Alba Petisco (ESP)
  - Anna Lashchevska (UKR)
  - Lena Bickel (SUI)
  - Hillary Heron (PAN)
  - Caitlin Rooskrantz (RSA)
  - Sona Artamonova (CZE)
  - Lihie Raz (ISR)
  - Lucija Hribar (SLO)
  


  
```{r}
# all athletes for teams
df_full_women_teams <- df_full %>%
  filter(Gender == 'w' &
         Country %in% c('USA', 'CAN', 'GER', 'ITA', 'AUS', 'KOR', 'ROU', 'NED', 
                        'HUN', 'CHN', 'JPN', 'GBR', 'BRA', 'MEX', 'FRA'))
```

```{r}
# break off criteria: athletes that have ranked at least top 5 for all countries
df_women_names <- df_full_women_teams %>%
  filter(Rank <= 5) %>%
  distinct(FullName) %>%
  pull()

df_women <- df_full_women_teams %>%
  filter(FullName %in% df_women_names)
```


```{r}
# individuals 
df_women_indv <- df_full %>%
  filter(FullName %in% c("NEMOUR KAYLIA", "SCHAEFER PAULINE", "MORENO ALEXA",
                         "MARTINS FILIPA", "FINNEGAN ALEAH", "CZIFRA BETTINA",
                         "PETISCO ALBA", "LASHCHEVSKA ANNA", "BICKEL LENA",
                         "HERON HILLARY", "ROOSKRANTZ CAITLIN", "ARTAMONOVA SONA",
                         "RAZ LIHIE", "HRIBAR LUCIJA"))
```


```{r}
# adding individuals, using distinct to remove overlaps 
df_women <- rbind(df_women, df_women_indv) %>% distinct(.keep_all = T)
```

```{r}
# writing to csv
write_csv(df_women, "cleaned data/restricted_women_2023.csv")
```


```{r}
df_women %>%
  mutate(top12_team = case_when(Country %in% c('USA', 'CAN', 'ITA', 'AUS', 
                                                'KOR', 'ROU', 'NED', 'CHN', 
                                                'JPN', 'GBR', 'BRA', 'FRA') ~ 1,
                                .default = 0),
         individual = case_when(FullName %in% c("NEMOUR KAYLIA", "SCHAEFER PAULINE", 
                                                    "MORENO ALEXA", "MARTINS FILIPA", 
                                                    "FINNEGAN ALEAH", "CZIFRA BETTINA", 
                                                    "PETISCO ALBA", "LASHCHEVSKA ANNA", 
                                                    "BICKEL LENA", "HERON HILLARY", 
                                                    "ROOSKRANTZ CAITLIN", "ARTAMONOVA SONA", 
                                                    "RAZ LIHIE", "HRIBAR LUCIJA") ~ 1,
                                .default = 0)) %>%
  filter(individual == 1)
```

```{r}
df_women %>%
  distinct(Competition)
```

